---
title: "Final year project R code"
author: "Scott Connors"
date: "09/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the data into R and loading packages.

```{r}
library(tidyverse)
library(quantreg)
require(gridExtra)

barnes_data <- read.delim("Predator_and_prey_body_sizes_in_marine_food_webs_vsn4.txt")
barnes_orig <- barnes_data
#changing all lengths to mm and weights to g
barnes_data <- transform(barnes_data, Predator.length = ifelse(Predator.length.unit == "cm", Predator.length*10, Predator.length))
barnes_data <- transform(barnes_data, Prey.length = ifelse(Prey.length.unit == "cm", Prey.length*10, Prey.length))
barnes_data <- transform(barnes_data, Predator.length = ifelse(Predator.length.unit == "µm", Predator.length/1000, Predator.length))
barnes_data <- transform(barnes_data, Prey.length = ifelse(Prey.length.unit == "µm", Prey.length/1000, Prey.length))
barnes_data <- transform(barnes_data, Prey.mass = ifelse(Prey.mass.unit == "mg", Prey.mass/1000, Prey.mass))
barnes_data$Predator.length.unit[barnes_data$Predator.length.unit == "cm"] <- "mm"
barnes_data$Prey.length.unit[barnes_data$Prey.length.unit == "cm"] <- "mm"
barnes_data$Predator.length.unit[barnes_data$Predator.length.unit == "µm"] <- "mm"
barnes_data$Prey.length.unit[barnes_data$Prey.length.unit == "µm"] <- "mm"
barnes_data$Predator.mass.unit[barnes_data$Predator.mass.unit == "mg"] <- "g"
```

Filtering out the four most common predator species in the data set.

```{r}
albfit <- barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.length, Prey.length, Predator.length.unit, Prey.length.unit, Predator.lifestage, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Albacore") %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))

dogfishfit <- barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.length, Prey.length, Predator.length.unit, Prey.length.unit, Predator.lifestage, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Spurdog / spiny dogfish") %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))

acodfit <- barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.length, Prey.length, Predator.length.unit, Prey.length.unit, Predator.lifestage, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Atlantic cod") %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))

ytunafit <- barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.length, Prey.length, Predator.length.unit, Prey.length.unit, Predator.lifestage, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Yellowfin tuna") %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))
```

Creating scatter plots with quantile regression lines.

```{r}
a <- ggplot(data = albfit, aes(x = Predator.length, y = Prey.length)) + geom_point() + geom_quantile(quantiles = 0.01) + geom_quantile(quantiles = 0.5) + geom_quantile(quantiles =  0.99) + ggtitle("Albacore")

b <- ggplot(data = dogfishfit, aes(x = Predator.length, y = Prey.length)) + geom_point() + geom_quantile(quantiles = 0.01) + geom_quantile(quantiles = 0.5) + geom_quantile(quantiles =  0.99) + ggtitle("Spiny Dogfish")

c <- ggplot(data = acodfit, aes(x = Predator.length, y = Prey.length)) + geom_point() + geom_quantile(quantiles = 0.01) + geom_quantile(quantiles = 0.5) + geom_quantile(quantiles =  0.99) + ggtitle("Atlantic Cod") 

d <- ggplot(data = ytunafit, aes(x = Predator.length, y = Prey.length)) + geom_point() + geom_quantile(quantiles = 0.01) + geom_quantile(quantiles = 0.5) + geom_quantile(quantiles =  0.99) + ggtitle("Yellowfin Tuna")

grid.arrange(a, b, c, d, ncol = 2, nrow = 2)
```

figuring out equations of regression lines.

```{r}

tau <- c(0.01, 0.5, 0.99)
qreg_fit <- rq(Prey.length ~ Predator.length, data = albfit, tau = tau)
summary(qreg_fit, se = "boot")
#   Max                            Median                   Min
# PY = 0.66462*PD - 269.48154 , PY = 0.06752*PD - 4.22560 , PY = 0.04697*PD - 14.38292

tau <- c(0.01, 0.5, 0.99)
qreg_fit <- rq(Prey.length ~ Predator.length, data = dogfishfit, tau = tau)
summary(qreg_fit, se = "boot")
#   Max                            Median                   Min
# PY = 0.33333*PD + 60 , PY = 0.12766*PD + 1.70213 , PY = 0.01364*PD + 0.86364

tau <- c(0.01, 0.5, 0.99)
qreg_fit <- rq(Prey.length ~ Predator.length, data = acodfit, tau = tau)
summary(qreg_fit, se = "boot")
#   Max                            Median                   Min
# PY = 0.42222*PD + 36.00000 , PY = 0.17391*PD - 12.17391 , PY = 0.02154*PD - 5.84615

tau <- c(0.01, 0.5, 0.99)
qreg_fit <- rq(Prey.length ~ Predator.length, data = ytunafit, tau = tau)
summary(qreg_fit, se = "boot")
#   Max                            Median                   Min
# PY = 0.10930*PD + 44.37209 , PY = 0.02222*PD + 7.11111 , PY = 0.00571*PD + 1.57143
```

Now creating histograms for showing that it is better to work with Log(PPMR) over PPMR.

```{r}
acodlogppmr.example <- barnes_data %>% select(Predator.common.name, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Atlantic cod") %>% mutate(PPMR = Predator.mass / Prey.mass, LogPPMR = log(Predator.mass / Prey.mass))
ytunalogppmr.example <- barnes_data %>% select(Predator.common.name, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Yellowfin tuna") %>% mutate(PPMR = Predator.mass / Prey.mass, LogPPMR = log(Predator.mass / Prey.mass))
albacorelogppmr.example <- barnes_data %>% select(Predator.common.name, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Albacore") %>% mutate(PPMR = Predator.mass / Prey.mass, LogPPMR = log(Predator.mass / Prey.mass))
dogfishlogppmr.example <- barnes_data %>% select(Predator.common.name, Predator.mass, Prey.mass) %>% group_by(Predator.common.name) %>% filter(Predator.common.name == "Spurdog / spiny dogfish") %>% mutate(PPMR = Predator.mass / Prey.mass, LogPPMR = log(Predator.mass / Prey.mass))
```

PPMR histograms.

```{r}
a <- ggplot(data = albacorelogppmr.example, aes(PPMR)) + geom_histogram(binwidth = 1000) + labs(title = "Albacore") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
b <- ggplot(data = dogfishlogppmr.example, aes(PPMR)) + geom_histogram(binwidth = 5000) + labs(title = "Spiny Dogfish") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
c <- ggplot(data = acodlogppmr.example, aes(PPMR)) + geom_histogram(binwidth = 10000) + labs(title = "Atlantic Cod") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
d <- ggplot(data = ytunalogppmr.example, aes(PPMR)) + geom_histogram(binwidth = 7500) + labs(title = "Yellowfin Tuna") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
grid.arrange(a, b, c, d, ncol = 2, nrow = 2)
```

Log(PPMR) histograms.

```{r}
a <- ggplot(data = albacorelogppmr.example, aes(LogPPMR)) + geom_histogram(binwidth = 0.08) + labs(title = "Albacore")
b <- ggplot(data = dogfishlogppmr.example, aes(LogPPMR)) + geom_histogram(binwidth = 0.09) + labs(title = "Spiny Dogfish")
c <- ggplot(data = acodlogppmr.example, aes(LogPPMR)) + geom_histogram(binwidth = 0.1) + labs(title = "Atlantic Cod")
d <- ggplot(data = ytunalogppmr.example, aes(LogPPMR)) + geom_histogram(binwidth = 0.1) + labs(title = "Yellowfin Tuna")
grid.arrange(a, b, c, d, ncol = 2, nrow = 2)
```

Coding the normal MLE's and density function into R for distributional fits.

```{r}
Mean_MLE <- function(n, logppmr) {
  MLEmean <- (1/n)*sum(logppmr)
  return(MLEmean)
}

SD_MLE <- function(n, logppmr, mean) {
  MLEsd <- sqrt((1/n)*sum((logppmr-mean)^2))
  return(MLEsd)
}
Ursin_Density <- function(logppmr, sd, mean) {
  Ursin_fit <- (exp(-(((logppmr - mean)^2)/(2*sd^2))))/(sd*sqrt(2*pi))
  return(Ursin_fit)
}
```

Creating Q_Q plots

```{r}
a <- ggplot(albfit, aes(sample = LogPPMR)) + ggtitle("Albacore") + stat_qq() + stat_qq_line()
b <- ggplot(dogfishfit, aes(sample = LogPPMR)) + ggtitle("Spiny Dogfish") + stat_qq() + stat_qq_line()
c <- ggplot(acodfit, aes(sample = LogPPMR)) + ggtitle("Atlantic Cod") + stat_qq() + stat_qq_line()
d <- ggplot(ytunafit, aes(sample = LogPPMR)) + ggtitle("Yellowfin Tuna") + stat_qq() + stat_qq_line()

grid.arrange(a, b, c, d, ncol = 2, nrow = 2)
```

Finding standard errors of ML estimators.

```{r}
## Finding MLE's
Mean_MLE(3581, albfit$LogPPMR)
SD_MLE(3581, albfit$LogPPMR, Mean_MLE(3581, albfit$LogPPMR))

Mean_MLE(3287, dogfishfit$LogPPMR)
SD_MLE(3287, dogfishfit$LogPPMR, Mean_MLE(3287, dogfishfit$LogPPMR))

Mean_MLE(2518, acodfit$LogPPMR)
SD_MLE(2518, acodfit$LogPPMR, Mean_MLE(2518, acodfit$LogPPMR))

Mean_MLE(2113, ytunafit$LogPPMR)
SD_MLE(2113, ytunafit$LogPPMR, Mean_MLE(2113, ytunafit$LogPPMR))

## General method for finding standard errors.

log_lik <- function(par_vec, x) {
  if(par_vec[2] < 0) return(1e8)
  lik <- dnorm(x,
               mean = par_vec[1],
               sd = par_vec[2])
   if(all(lik == 0)) return(1e8)
  return(-sum(log(lik[lik != 0])))
}


coef_est <- optim(par = c(0,0),
      fn = log_lik, hessian = T,
      x = X)

print(sqrt(diag(solve(coef_est$hessian))))

## Albacore 
X <- albfit$LogPPMR

coef_est <- optim(par = c(9.546003,1.146738),
      fn = log_lik, hessian = T,
      x = X)

print(coef_est)
print(sqrt(diag(solve(coef_est$hessian))))

## 0.01916294 0.01355020

## Spiny Dogfish
X <- dogfishfit$LogPPMR

coef_est <- optim(par = c(5.537637,2.193598),
      fn = log_lik, hessian = T,
      x = X)

print(coef_est)
print(sqrt(diag(solve(coef_est$hessian))))

## 0.03826108 0.02705464

## Atlantic Cod
X <- acodfit$LogPPMR

coef_est <- optim(par = c(5.725514,2.600442),
      fn = log_lik, hessian = T,
      x = X)

print(coef_est)
print(sqrt(diag(solve(coef_est$hessian))))

## 0.05182261 0.03664411

## Yellowfin Tuna
X <- ytunafit$LogPPMR

coef_est <- optim(par = c(10.16201,1.802751),
                   fn = log_lik, hessian = T,
                   x = X)

print(coef_est)
print(sqrt(diag(solve(coef_est$hessian))))

## 0.03921805 0.02773131
```

Creating normal fits.

```{r}
a <- albfit %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 3581 , args = list(mean = Mean_MLE(3581, albfit$LogPPMR), sd = SD_MLE(3581, albfit$LogPPMR,  Mean_MLE(3581, albfit$LogPPMR))))+ ggtitle("Albacore") + expand_limits(x = c(0,17))



b <- dogfishfit %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 3287 , args = list(mean = Mean_MLE(3287, dogfishfit$LogPPMR), sd = SD_MLE(3287, dogfishfit$LogPPMR,  Mean_MLE(3287, dogfishfit$LogPPMR))))+ ggtitle("Spiny Dogfish")+ expand_limits(x = c(0,17))


c <- acodfit %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 2518 , args = list(mean =  Mean_MLE(2518, acodfit$LogPPMR), sd = SD_MLE(2518, acodfit$LogPPMR,  Mean_MLE(2518, acodfit$LogPPMR))))+ ggtitle("Atlantic Cod")+ expand_limits(x = c(0,17))



d <- ytunafit %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 2113 , args = list(mean = Mean_MLE(2113, ytunafit$LogPPMR), sd = SD_MLE(2113, ytunafit$LogPPMR,  Mean_MLE(2113, ytunafit$LogPPMR))))+ ggtitle("Yellowfin Tuna")+ expand_limits(x = c(0,17))

grid.arrange(a, b, c, d, ncol = 2, nrow = 2)
```

Creating skewness and curtosis plot for Albacore.

```{r}
library(fitdistrplus)
descdist(albfit$LogPPMR, boot = 1000)
```

Fitting 5 dists over a histogram of Log(PPMR) Albacore data & using summary to check AIC values for each fit.

```{r}
fln <- fitdist(albfit$LogPPMR, "lnorm")
fg <- fitdist(albfit$LogPPMR, "gamma")
fwb <- fitdist(albfit$LogPPMR, "weibull")
fn <- fitdist(albfit$LogPPMR, "norm")
fl <- fitdist(albfit$LogPPMR, "logis")

summary(fln)
summary(fg)
summary(fwb)
summary(fn)
summary(fl)

plot.legend <- c("lognormal", "gamma", "normal", "weibull", "logistic")
denscomp(list(fln, fg, fn, fwb, fl), legendtext = plot.legend)
```

testing adult and juvenile ppmr values.

```{r}
yellowfin_pre_mature <- ytunafit %>% filter(Predator.mass < 33000)
yellowfin_post_mature <- ytunafit %>% filter(Predator.mass >= 33000)

acod_pre_mature <- acodfit %>% filter(Predator.length < 410)
acod_post_mature <- acodfit %>% filter(Predator.length >= 410)


sdog_pre_mature <- dogfishfit %>% filter(Predator.length < 685)
sdog_post_mature <- dogfishfit %>% filter(Predator.length >= 685)

##plots

a <- yellowfin_post_mature %>% ggplot(aes(x = LogPPMR)) + stat_function(fun = dnorm, n = 777 , args = list(mean = Mean_MLE(777, yellowfin_post_mature$LogPPMR), sd = SD_MLE(777, yellowfin_post_mature$LogPPMR,  Mean_MLE(777, yellowfin_post_mature$LogPPMR))), colour = "red") + stat_function(fun = dnorm, n = 1336 , args = list(mean = Mean_MLE(1336, yellowfin_pre_mature$LogPPMR), sd = SD_MLE(1336, yellowfin_pre_mature$LogPPMR,  Mean_MLE(1336, yellowfin_pre_mature$LogPPMR))), colour = "blue") + stat_function(fun = dnorm, n = 2113 , args = list(mean = Mean_MLE(2113, ytunafit$LogPPMR), sd = SD_MLE(2113, ytunafit$LogPPMR,  Mean_MLE(2113, ytunafit$LogPPMR)))) + ggtitle("Yellowfin Tuna") + expand_limits(x = c(0,17)) + ylab("density")

b <- acod_post_mature %>% ggplot(aes(x = LogPPMR)) + stat_function(fun = dnorm, n = 2266 , args = list(mean = Mean_MLE(2266, acod_post_mature$LogPPMR), sd = SD_MLE(2266, acod_post_mature$LogPPMR,  Mean_MLE(2266, acod_post_mature$LogPPMR))), colour = "red") + stat_function(fun = dnorm, n = 252 , args = list(mean = Mean_MLE(252, acod_pre_mature$LogPPMR), sd = SD_MLE(252, acod_pre_mature$LogPPMR,  Mean_MLE(252, acod_pre_mature$LogPPMR))), colour = "blue") + stat_function(fun = dnorm, n = 2518 , args = list(mean =  Mean_MLE(2518, acodfit$LogPPMR), sd = SD_MLE(2518, acodfit$LogPPMR,  Mean_MLE(2518, acodfit$LogPPMR)))) + ggtitle("Atlantic Cod") + expand_limits(x = c(0,17)) + ylab("density")

c <- sdog_post_mature %>% ggplot(aes(x = LogPPMR)) + stat_function(fun = dnorm, n = 2825 , args = list(mean = Mean_MLE(2825, sdog_post_mature$LogPPMR), sd = SD_MLE(2825, sdog_post_mature$LogPPMR,  Mean_MLE(2825, sdog_post_mature$LogPPMR))), colour = "red") + stat_function(fun = dnorm, n = 462 , args = list(mean = Mean_MLE(462, sdog_pre_mature$LogPPMR), sd = SD_MLE(462, sdog_pre_mature$LogPPMR,  Mean_MLE(462, sdog_pre_mature$LogPPMR))), colour = "blue") + stat_function(fun = dnorm, n = 3287 , args = list(mean = Mean_MLE(3287, dogfishfit$LogPPMR), sd = SD_MLE(3287, dogfishfit$LogPPMR,  Mean_MLE(3287, dogfishfit$LogPPMR)))) + ggtitle("Spiny Dogfish") + expand_limits(x = c(0,17)) + ylab("density")

grid.arrange(a, b, c, ncol = 3)

```

Testing how statistically significant the differences in adult and juvenile means are.

```{r}
t.test(x = ytunafit$LogPPMR, alternative = "two.sided", mu = 10.32082, var.equal = FALSE, conf.level = 0.05) #post mature
t.test(x = ytunafit$LogPPMR, alternative = "two.sided", mu = 10.06965, var.equal = FALSE, conf.level = 0.05) #pre mature

t.test(x = acodfit$LogPPMR, alternative = "two.sided", mu = 5.723287, var.equal = FALSE, conf.level = 0.05)
t.test(x = acodfit$LogPPMR, alternative = "two.sided", mu = 5.745541, var.equal = FALSE, conf.level = 0.05)

t.test(x = dogfishfit$LogPPMR, alternative = "two.sided", mu = 5.588913, var.equal = FALSE, conf.level = 0.05)
t.test(x = dogfishfit$LogPPMR, alternative = "two.sided", mu = 5.224098, var.equal = FALSE, conf.level = 0.05)
```

Testing how the normal distribution fits to filter feeders and longfin squid.

```{r}
barnes_cephalopod <- barnes_data %>% 
     select(Predator.common.name,Predator..taxon , Prey.common.name, Predator.mass, Prey.mass, Mean.annual.temp, Geographic.location) %>% 
     group_by(Predator.common.name) %>% filter(Predator..taxon == "cephalopod") %>%
     mutate(LogPPMR = log(Predator.mass / Prey.mass))


SANDFIT <-  barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.mass, Prey.mass, Mean.annual.temp, Geographic.location)  %>% filter(Predator.common.name == "Pacific sandlance")%>% group_by(Predator.common.name) %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))

PHFIT <-  barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.mass, Prey.mass, Mean.annual.temp, Geographic.location)  %>% filter(Predator.common.name == "Pacific herring")%>% group_by(Predator.common.name) %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))

APFIT <-  barnes_data %>% select(Predator.common.name, Prey.common.name, Predator.mass, Prey.mass, Mean.annual.temp, Geographic.location)  %>% filter(Predator.common.name == "Alaskan pollack") %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))


## Plots


a <- SANDFIT %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 136 , args = list(mean = Mean_MLE(136, SANDFIT$LogPPMR), sd = SD_MLE(136, SANDFIT$LogPPMR,  Mean_MLE(136, SANDFIT$LogPPMR))))+ ggtitle("Pacific Sandlance") + expand_limits(x = c(0,17))

b <- APFIT %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 162 , args = list(mean = Mean_MLE(162, APFIT$LogPPMR), sd = SD_MLE(162, APFIT$LogPPMR,  Mean_MLE(162, APFIT$LogPPMR))))+ ggtitle("Atlantic Pollock") + expand_limits(x = c(0,17))


c <- PHFIT %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") +
  stat_function(fun = dnorm, n = 28 , args = list(mean = Mean_MLE(28, PHFIT$LogPPMR), sd = SD_MLE(28, PHFIT$LogPPMR,  Mean_MLE(28, PHFIT$LogPPMR))))+ ggtitle("Pacific Herring") + expand_limits(x = c(0,17))

d <- barnes_cephalopod %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") + stat_function(fun = dnorm, n = 113 , args = list(mean = Mean_MLE(113, barnes_cephalopod$LogPPMR), sd = SD_MLE(113, barnes_cephalopod$LogPPMR,  Mean_MLE(113, barnes_cephalopod$LogPPMR))))+ ggtitle("Longfin squid") + expand_limits(x = c(0,17))

grid.arrange(a, b, c, d, ncol = 2, nrow = 2)
```

Testing the relationship between temperature and PPMR.

```{r}
min_10.predators <- barnes_data %>% filter(Mean.annual.temp < 10) %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))
bot.mid.temp.predators <- barnes_data %>% filter(Mean.annual.temp >= 10 & Mean.annual.temp < 15) %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))
up.mid.temp.predators <- barnes_data %>% filter(Mean.annual.temp >= 15 & Mean.annual.temp < 20) %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))
high.temp.predators <- barnes_data %>% filter(Mean.annual.temp > 20) %>% mutate(LogPPMR = log(Predator.mass / Prey.mass))

## Empirical density plots

a <- min_10.predators %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") + ggtitle("< 10deg ") + coord_cartesian(xlim =c(0, 17))

b <- bot.mid.temp.predators %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") + ggtitle("10deg to < 15deg") + coord_cartesian(xlim =c(0, 17))

c <- up.mid.temp.predators %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") + ggtitle("15deg to < 20deg") + coord_cartesian(xlim =c(0, 17))

d <- high.temp.predators %>% ggplot(aes(x = LogPPMR)) + geom_density(fill = "lightblue") + ggtitle("> 20deg") + coord_cartesian(xlim =c(0, 17))

grid.arrange(a, b, c, d, nrow = 4)

# Log(PPMR) means by temp

mean(min_10.predators$LogPPMR)
10.36361

mean(bot.mid.temp.predators$LogPPMR)
6.718306

mean(up.mid.temp.predators$LogPPMR)
6.32164

mean(high.temp.predators$LogPPMR)
8.960437

# Overall mean

mean(barnes_data$LogPPMR)
7.008117

```