---
title: "Global patterns in predator—prey size relationships, Analysis"
author: "Scott Connors"
date: "28/10/2020"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysing prey of Haddock data

For this assignment I have decided to use data from the DAPSTOM database, found here (https://www.cefas.co.uk/data-and-publications/fish-stomach-records/), specifically data regarding prey types of Haddock to make some simple plots and analysis.

## Preparing & plotting the data

First I need to load any packages I will use for the analysis, and the data from the DAPSTOM database about haddock needs to be read into R.

```{r, message=FALSE}
library(tidyverse)
haddock_data <- read_csv("Haddock_Data.csv")
```

I first plan on looking at the `Mean length of predator` data, so to check visually for any possible errors I plot the data as below. It would appear that there are no obvious errors within the dataset. 

```{r}
plot(haddock_data$`Mean length of predator`)
```

I want to create a tibble containing the mean length of Haddock grouped by year, so that eventually I can create a simple plot analysing the average length of the Haddock recorded for each year. I do this as below using functions such as `group_by()` and `summarise()`. 

```{r, message=FALSE}
annual_mean_length <- haddock_data %>% group_by(Year) %>% summarise(annual_predator_length = mean(`Mean length of predator`))
```

Now that I have created the data I want to plot, I can make the graph using the `ggplot()` function and see that in some years the Haddock recorded in the database were much bigger on average than in other years. Perhaps this is just because more data was collected in some years compared to other years. 

```{r}
annual_mean_length %>% ggplot(aes(x=Year, y=annual_predator_length)) + geom_point() + geom_line() + ylab("Annual Mean Length [cm]")
```

## Prey types in different Sea's

Now I'd like to look at what types of prey the Haddock is eating depending on what Sea it lives in. So, I can group the data by `Prey common name` & `Sea` and use the `count()` function to make a tibble of the amounts of each prey type sorted by `Sea`.

```{r}
prey_number <- haddock_data %>% group_by(`Prey common name`, Sea) %>% count()
prey_number
```

Because there are a lot of prey types I'm going to remove Prey with less than 10 entries using `filter()`. 

```{r}
prey_number_10 <- prey_number %>% filter(n > 10)
prey_number_10
```

Next I need to remove the EPMTY `Prey common name` values as this won't provide us with much useful insight one plotted.

```{r}
prey_number_10 <- prey_number_10[-c(10,11),]
```

Finally using `ggplot()` again I can plot the prey types against amounts on separate plots for each sea using `facet_wrap()`. I've decided to put the prey names on the Y axis simply because they won't overlap each other. Looking at the plot's I can see for example that there are much more `MOLLUSCA-BIVALVIA` and `BRISTLE WORMS` eaten by Haddock in the Celtic Sea compared to the Irish Sea. Could this be because the Haddock seem to rely very heavily on eating `NORWAY LOBSTER` in the Irish Sea?

```{r, message=FALSE}
prey_number_10 %>% ggplot(aes(x = n, y = `Prey common name`)) + geom_point() + geom_line() + facet_wrap(~Sea)
```