---
title: "Reproduction of Barnes data in the style of Ursin"
author: "Scott Connors"
date: "17/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the data into R and loading packages.

```{r}
library(fitdistrplus)
library(tidyverse)
barnes_data <- read.delim("Predator_and_prey_body_sizes_in_marine_food_webs_vsn4.txt")
#changing all lengths to mm and weights to g
barnes_data <- transform(barnes_data, Predator.length = ifelse(Predator.length.unit == "cm", Predator.length*10, Predator.length))
barnes_data <- transform(barnes_data, Prey.length = ifelse(Prey.length.unit == "cm", Prey.length*10, Prey.length))
barnes_data <- transform(barnes_data, Predator.length = ifelse(Predator.length.unit == "µm", Predator.length/1000, Predator.length))
barnes_data <- transform(barnes_data, Prey.length = ifelse(Prey.length.unit == "µm", Prey.length/1000, Prey.length))
barnes_data <- transform(barnes_data, Prey.mass = ifelse(Prey.mass.unit == "mg", Prey.mass/1000, Prey.mass))
barnes_data$Predator.length.unit[barnes_data$Predator.length.unit == "cm"] <- "mm"
barnes_data$Prey.length.unit[barnes_data$Prey.length.unit == "cm"] <- "mm"
barnes_data$Predator.length.unit[barnes_data$Predator.length.unit == "µm"] <- "mm"
barnes_data$Prey.length.unit[barnes_data$Prey.length.unit == "µm"] <- "mm"
barnes_data$Predator.mass.unit[barnes_data$Predator.mass.unit == "mg"] <- "g"
```

Filtering the data to only include data for the predator Atlantic cod, and looking at some quantities.

```{r}
atlantic.cod <- barnes_data %>% filter(Predator.common.name=="Atlantic cod")
atlantic.cod.mean <- atlantic.cod %>% summarise(mean(Predator.mass))
atlantic.cod.prey.mean <- atlantic.cod %>% summarise(mean(Prey.mass))
```

## Replicating the size frequency plot for prey


eliminating all other columns apart from the ones I need for this plot.

```{r}
barnes.data.sorted <- barnes.data %>% select(Predator.common.name, Prey.common.name, prey.mass, predator.mass)
prey.data.grams <- barnes.data.sorted %>% select(Prey.common.name, Prey.mass, Predator.common.name, Predator.mass) #completely unnecessary, not sure why I did this.
```

counting the amount of each prey and taking the mean weight per prey type.

```{r}
cod.prey.count <- prey.data.grams %>% group_by(Prey.common.name) %>% count()
cod.prey.mean <- prey.data.grams %>% group_by(Prey.common.name) %>% summarise(mean(Prey.mass))
```

Combining the count and mean data into one table.

```{r}
size.frequency.grams <- full_join(prey.mean, prey.count)
size.frequency.grams <- size.frequency.grams %>% rename(mean.weight.g = "mean(Prey.mass)")
```

adding a column of the expected count of each prey type using N=Nw^-1

```{r}
size.frequency.grams <- size.frequency.grams %>% mutate(expected.count = n*mean.weight.g^-1)
```

Creating the log weight against log expected numbers numbers plot, which does show the expected shape.

```{r}
frequency.plot.grams <- size.frequency.grams %>% ggplot(aes(x = log(mean.weight.g), y = log(expected.count))) + geom_point() + geom_smooth(method = 'lm') + ylab("log expected numbers") + xlab("log weight grams") + ggtitle("Size Frequency Plot")
```



## Fitting the normal distribution to the log(pred/prey) mass ratio of the Atlantic cod data in the Barnes dataset


Calculating the log(pred/prey) mass ratio.

```{r}
log.pred.w.over.prey.w <- log((atlantic.cod$Predator.mass)/(atlantic.cod$Prey.mass))
```

Finding mean and standard deviation of log(pred/prey) ratio.

```{r}
mean(log.pred.w.over.prey.w)
5.675068

sd(log.pred.w.over.prey.w)
2.69574
```

Applying Ursins formula (5).

```{r}
y <- (exp(-((log.pred.w.over.prey.w - 5.675068)^2)/(2*(2.69574)^2)))/ (2.69574*sqrt(2*pi))

plot(log.pred.w.over.prey.w, y)
```